---
title: "Enzyme Activity Analysis Script"
author: "Maddie Heard"
date: "4/30/2018"
output: html_document
---

#Load your data! If analyzing day 1, use a subset of data with only day 1 values because na.omit will remove these values from the analysis. For analyzing day 5 you can keep all data because the day 1 values will be removed once you na.omit.
```{r}
activity<-read.csv(file.choose())
#d1<-activity
d5<-activity
summary(d5)
names(d5)
View(d5)
length(d5)
```


#Summary stats and tests for normality!
```{r}
#this shows the normality of the data (p<0.05 means data is not normal - must transform!)
#CS - sqrt works 
#LDH - 
xform = sqrt
shapiro.test(xform(d5$ratio_activity))
#this also shows normality. The more points on the line the more normal data is.
qqnorm(xform(d5$ldh_activity))
qqline(xform(d5$cs_activity))
hist(xform(d5$ratio_activity))
mean(xform(d5$cs_activity))
sd(xform(d5$cs_activity))
```


There are a lot of NA's at the end of this data frame so let's remove them....

#remove NAs from data
```{r}
#may not need this?
d5_na<-na.omit(d5)
#check to see if NAs still remain
View(d5_na)
```

#summary statistics on cleaned-up data frame using base R (but also gets rid of day 1 samples)
```{r}
summary(d5_na)
summary(d1$cs_activity)
mean(d5_na$cs_activity)
sd(d5_na$cs_activity)
hist(d5_na$cs_activity, main = "Histogram of CS Activity on Day 5", xlab="CS Activity (IU/gfw)")
```




#Activity at Day 1 separated by treatment and averaging over maternal variability
```{r}
library(ggplot2)
ggplot(data=d5_na,aes(y=sqrt(ratio_activity),x=d5_treat))+
  geom_boxplot(aes(color=d5_treat))+
  ggtitle("Ratio Activity on Day 5 by Treatment")+ #change enzyme name
  xlab("Treatment")+
  ylab("Ratio Activity (IU/gfw)")+ #change enzyme name
  theme_bw()
#coord_flip makes this graph horizontal
  #+ coord_flip()
ggsave("cs_d1_treat.pdf",width=8, height=5) #change enzyme name
```



#Activity at Day 1 separated by treatment and mother
```{r}
library(ggplot2)
ggplot(data=d5_na,aes(y=sqrt(ratio_activity),x=d5_treat))+
  geom_boxplot(aes(color=d5_treat, mother))+
  ggtitle("Ratio Activity on Day 5 by Mother and Treatment")+
  xlab("Mother")+
  ylab("Ratio Activity (IU/gfw)")+
  theme_bw()
ggsave("ratio_d1_treat_mother.pdf",width=8, height=5)
```




#Activity at Day 5 separated by treatment for each mother
```{r}
ggplot(data=d5_na,aes(y=ratio_activity,x=d5_treat))+ #change enzyme name
  geom_boxplot(aes(color=d5_treat, mother))+ #how to I show individual mothers that contirbuted to each treatment?
  ggtitle("Ratio Activity on Day 5 per Treatment")+ #change enzyme name
  xlab("Treatment")+
  ylab("Ratio Activity (IU/gfw)")+ #change enzyme name
  theme_bw()
ggsave("ratio_d5_treatmom.pdf",width=8, height=5) #change enzyme name
```



#Activity at Day 5 separated by treatment and mother
```{r}
library(ggplot2)
ggplot(data=d5_na,aes(y=ratio_activity,x=d5_treat))+
  geom_boxplot(aes(color=mother))+
  ggtitle("Ratio Activity on Day 5 by Mother and Treatment")+
  xlab("Treatment")+
  ylab("Ratio Activity")+
  theme_bw()
ggsave("ratio_d5_treat_mother.pdf",width=8, height=5)
```


















Below this is Jake's code to run using my data. Still needs to be fixed.

```{r}
## Jake's Enzyme and Hematocrit Data Analysis Code, using ANOVA
#change the file pathway to your own
getwd()
setwd("/Users/madisonheard/github/gopher_larvae")

#to run ratio activity data
mydata = read.csv("ratio_activity_R.csv", header=TRUE,stringsAsFactors = FALSE)
mydata

mydata<-mydata[,1:5]
mydata
```

```{r}
# Install this package to make use of the %>% pipe operator and other stuff.
install.packages("magrittr")
library(magrittr)
```


```{r}

# Install this package to use group_by and other stuff.
install.packages("dplyr")
library(dplyr)

#my project will need to be grouped some other way -- maybe mother?
#Average function? What does this mean?
group_by(mydata, mother) %>%
     summarize(
         count = n(),
         mean = mean(ratio_activity, na.rm=TRUE),
         sd = sd(ratio_activity, na.rm=TRUE)
     )
#to create a table with only ratio_activity, mother and the larval treatment columns
ratio<-mydata%>%
  select(ratio_activity, mother, d1_treat, d5_treat)
View(ratio)

```


```{r}
boxplot(sd~mydata$mother)
```






```{r}
#STILL NEED TO FIX THE REST OF THIS CODE
## To manually reorder the treatments in the boxplot:


mydata$mother = factor(mydata$mother)
boxplot(ratio_activity ~ mother, mydata)

mydata$Treatment = factor(mydata$Treatment,c("C","M","E","R","U")) 
    
boxplot(Average ~ Treatment, mydata, range = 0, main="Humboldt Year 3 - Upwelling\nBlack Rockfish Hematocrit", xlab="Treatment",ylab="Hematocrit (Erythrocyte %)",ylim=c(.3,.6))
```


```{r}
# To add dots representing the means. Boxplots show the median, quartiles and min&max.

means <- by(mydata$Average, mydata$Treatment, mean)
points(1:5, means, pch = 21, cex =1.5, bg = "blue")
```


```{r}
## ANOVA Code

humboldt_aov=aov(Average~Treatment,mydata)
summary(humboldt_aov)

```

```{r}
## Tukey post-hoc pairwise comparisons of means

TukeyHSD(humboldt_aov)
```


