---
title: "Data wrangling"
author: "Maddie Heard"
date: "4/18/2018"
output: html_document
---

Load libaries
```{r}
#install.packages("tidyverse")
library(tidyverse)
```

Read in data
```{r}
ldh<-read_csv("ldh_activity_R.csv")
View(ldh)
ldh<-ldh[,1:5]
names(ldh)
```

Select columns of interest using `select`
```{r}
ldh<-ldh%>%
  select(ldh_activity, mother, d1_treat, d5_treat)
```

Remove NAs in 'ldh_activity' column only
```{r}
ldh<-ldh%>%
  drop_na(ldh_activity)

View(ldh)
```


Run ANOVA on each mom's dataset using `group_by`
*Note ***this is not working yet...(may need to change column format?): ask Judith**
```{r, eval = FALSE}
ldh_mom <- ldh %>%
  group_by(mother) %>%
  aov(ldh_activity~factor(d1_treat)*factor(d5_treat)) %>%
  anova()
``` 
 
 Try different approach...
 
 Run ANOVA on a single mother. First filter out single mom's dataset
```{r}
ldh_G79 <- ldh %>%
  filter(mother=="G79")  # pull out data from a single mom
  # drop_na  # remove na's to remove day 1 only data

head(ldh_G79)
```

Try ANOVA -- **Maddie: ask Judith about this. I'm not sure I've set up the test correctly**
```{r, eval = FALSE}
model <- aov(data=ldh_G79,ldh_activity~factor(d1_treat)*factor(d5_treat))
anova(model)

head(ldh_G79)
```

Try running ANOVA on full dataset - **this works**, but it's not filtered by mother
```{r}
model<-aov(data=ldh,ldh_activity~factor(d1_treat)*factor(mother))
anova(model)
```

